Towards Adaptive GPU Resource Management for Embedded Real-Time Systems

### 2012-03-15 draft/draft.tex
recovered the citations related to self-driving cars

One notable application domain of GPUs is automotive engineering.
Modern automobiles employ several tens of processing units.
Further advances in safe-driving features, such as adaptive
cruise control, stop-and-go cruise control, lane keeping, and assisted
lane change, would require even larger computing capabilities.
%As vehicles are becoming autonomous, 
For vehicles to become fully or semi-autonomous, 
a multitude of computer vision,
sensor fusion, signal processing, and graphics sub-systems must operate and
communicate in real-time.
Given their highly data-parallel and compute-intensive workloads, 
parallel computing is a useful solution.
As technology stands today, the GPU is the most well-suited platform.
In fact, NVIDIA GPUs will be used for infotainment systems platforms in
future product lines of BMW vehicles~\cite{NVIDIA_BMW}.

>>>>

One notable application domain of GPUs is automotive engineering.
Modern automobiles employ several tens of processing units.
Further advances in safe-driving features, such as adaptive
cruise control, stop-and-go cruise control, lane keeping, and assisted
lane change, would require even larger computing capabilities.
%As vehicles are becoming autonomous, 
For vehicles to become fully or semi-autonomous, 
a multitude of computer vision,
sensor fusion, signal processing, and graphics sub-systems must operate and
communicate in real-time~\cite{Kelly12, Markoff10, Urmson08}.
Given their highly data-parallel and compute-intensive workloads, 
parallel computing is a useful solution.
As technology stands today, the GPU is the most well-suited platform.
In fact, NVIDIA GPUs will be used for infotainment systems platforms in
future product lines of BMW vehicles~\cite{NVIDIA_BMW}.
